\begin{thebibliography}{99}

\bibitem{JAPSHA11}
  N. Japkowicz, M. Shah,
  \emph{Evaluating Learning Algorithms - A Classification Perspective},
  Cambridge University Press,
  2011.

\bibitem{SANTAFE15}
  G. Santafé, I. Inza, J. A. Lozano,
  \emph{Dealing with the evaluation of supervised classification algorithms},
  Springer Science - AIRE,
  2015.
  
\bibitem{PRATI11}
  R. C. Prati, G. E.A.P.A. Batista, M. C. Monard,
  \emph{A Survey on Graphical Methods for Classification Predictive Performance Evaluation},
  IEEE TRANSACTIONS ON KNOWLEDGE AND DATA ENGINEERING, VOL. 23, NO. 11,
  2011

\bibitem{DICCHA11}
  J. Dickinson Gibbons, S. Chakraborti,
  \emph{Nonparametric Statistical Inference},
  Fifth edition,
  Chapman and Hall/CRC,
  2011
	
\bibitem{SHESKIN11}
  D. J. Sheskin,
  \emph{Handbook of Parametric and Nonparametric Statistical Procedures},
  Fourth edition,
  Chapman and Hall/CRC,
  2007
  
\bibitem{PESSAL10}
	F. Pesarin, L. Salmaso,
	\emph{Permutation Test for Complex Data}
	WILEY, 
	2010
  
\bibitem{KANUNGO00}
	T. Kanungo, R. M. Haralick, H. S. Baird, W. Stuezle, D. Madigan,
  \emph{A Statistical, Nonparametric Methodology for Document Degradation Model Validation},
  IEEE Transactions on Pattern Analysis and Machine Intelligence,
  VOL. 22, NO. 11,
  2000
  
\bibitem{CHENGCHEN03}
	Xiuzhen Cheng, Dechang Chen
  \emph{Statistical Comparisons of Multiple Classifiers},
  2003
  
\bibitem{DEMSAR06}
	J. Dem\v{s}ar
	\emph{Statistical Comparisons of Classifiers over Multiple Data Sets},
	Journal of Machine Learning Research 7,
	2006
	
	
\bibitem{GARCIAHERRERA08}
	S. García, F. Herrera,
	\emph{An Extension on ``Statistical Comparisons of Classifiers over Multiple Data Sets'' for all Pairwise Comparisons},
	Journal of Machine Learning Research 9,
	2008
	
\bibitem{GARCIA09}
	S. García, D. Molina, M. Lozano, F. Herrera
	\emph{A study on the use of non-parametric test for analyzing the evolutionary algorithms' behaviour: a case study on the CEC'2005 Special Session on Real Parameter Optimization},
	Journal of Heuristics,
	2009

\bibitem{GARCIA08}
	S. García, A. Fernández, J. Luengo, F. Herrera
	\emph{A study of statistical techniques and performance measures for genetics-based machine learning: accuracy and interpretability},
	Springer-Verlag,
	2008
	
\bibitem{OTERO13}
	J. Otero, L. Sánchez, I. Couso, A. Palacios.,
	\emph{Bootstrap analysis of multiple repetitions of experiments using an interval-valued multiple comparison procedure}
	Elsevier, Journal of Compuyer and System Sciences,
	NO. 80,
	2013

\bibitem{ALPAYDIN10}
	E. Alpaydin,
	\emph{Introduction to Machine Learning},
	2a. Edición, 
	The MIT Press,
	2010

\bibitem{HOLLANDER14}
	M. Hollander, D.A. Wolfe, E. Chicken,
	\emph{Nonparametric Statistical Methods},
	3a. Edición,
	Wiley,
	2014
	
\end{thebibliography}